---
title: "Emotion Classification Analysis (Manuscript)"
author: "Joey Heffner"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

# Setup
To run this analysis script you'll have to have the following packages installed (make sure `tidyverse` is updated): 

|Packages1  |Packages2    |Packages3 |Packages4    |
|:---------:|:-----------:|:--------:|:-----------:|
|`here`     |`tidyverse`  |`knitr`   |`kableExtra` |
|`purr`     |`lme4`       |`lmerTest`|`broom.mixed`|
|`ggrepel`  |`sjPlot`     |`ggridges`|

To install these packages simply use the `install.packages()` function and put each package name in as a string. 

**Note**: If you've already used the `here()` function in another script, you will have to open a new instance of R to ensure the relative paths works for this script (or manually change the paths).

The order of this Markdown will follow the order of results in the Manuscript which is published in Nature Communications at the following [DOI]().

```{r setup, include=FALSE}
# Knitr options
knitr::opts_chunk$set(echo = FALSE, warnings = FALSE, message = FALSE)

# Save plots or not
#save_plots <- FALSE  # if you want to generate new plots make TRUE
load_models <- TRUE   # if you want to load the pre-trained models

# Libraries
library(here)         # relative paths
library(tidyverse)    # tidy functions
library(knitr)        # knit functions
library(kableExtra)   # extra markdown functions
library(purrr)        # map functions
library(lme4)         # mixed-effects regressions
library(lmerTest)     # mixed-effects regressions
library(AICcmodavg)   # predictSE()
library(broom.mixed)  # tidy()
library(ggrepel)      # geom_text_repel
library(sjPlot)       # tab_model
library(rstatix)      # cohen's d
library(ggridges)     # density plot

## Data
# Specify relative paths
dir_analysis <- here()
dir_parent <- str_remove(dir_analysis, "/analysis")
dir_clean_data <- str_c(dir_parent, "/data/behavioral")
dir_models <- str_c(dir_parent, "/data/oscar")
dir_data <- str_c(dir_parent, "/data")
dir_graphs <- str_c(dir_parent, "/graphs")
dir_supplement <- str_c(dir_parent, "/graphs/supplement")
```

# Data 

The descriptions for each column of the two dataframes can be found below: 

## Emotion Classification Task

- `sub`: unique subject identifier
- `trial`: trial number of the `emotion` rating (20 trials)
- `emotion`: feeling label being rated on the emotion measure (dARM)
- `valence`: unpleasant (-) or pleasant (+) rating of `emotion` (range -250 to +250)
- `arousal`:  low (-) or high (+) rating on `emotion` (range -250 to +250)
- `study`: refers to whether the data was from the `ug`, `pd`, or `pgg` experiment

## Ultimatum Game

- `sub`: unique subject identifier
- `trial`: trial number of the ultimatum game (20 trials) 
- `unfairness`: the amount of money kept by the Proposer (out of `1`), ranges equally from fair (Proposer kept `.50`) to severely unfair (Proposer kept `.95`) in increments of `.05`. Each unfairness type is given twice.
- `valence`: unpleasant (-) or pleasant (+) rating in response to `How do you feel about the Proposer's offer?` (range -250 to +250)
- `arousal`:  low (-) or high (+) rating in response to `How do you feel about the Proposer's offer?` (range -250 to +250)
- `choice`: 0 is accept, 1 is reject
- `study`: refers to whether the data was from the `ug`, `pd`, or `pgg` experiment

## Prisoners' Dilemma

- `sub`: unique subject identifier
- `trial`: trial number of the prisoners' dilemma (22 trials) 
- `partner_contribution`: the amount of money given to the common good by their partner, ranges equally from defection (0) to cooperation (1) in increments of `.1`. Each contribution type is given twice. 
- `valence`: unpleasant (-) or pleasant (+) rating in response to `How do you feel about your partner's contribution?` (range -250 to +250)
- `arousal`:  low (-) or high (+) rating in response to `How do you feel about your partner's contribution?` (range -250 to +250)
- `sub_contribution`: the amount of money given to the common good by the subject, ranges from 0 - 1 in increments of `.1`.
- `sub_contribution_binary`: `sub_contribution` was converted into a binary variable with defect (0 - .49) and cooperate (.50 - 1). 
- `study`: refers to whether the data was from the `ug`, `pd`, or `pgg` experiment

## Public Goods Game

- `sub`: unique subject identifier
- `trial`: trial number of the public goods game (22 trials) 
- `partner_contribution`: the amount of money given to the common good by their partners (collectively), ranges equally from defection (0) to cooperation (3) in increments of `.1`. Each contribution type is given twice. 
- `valence`: unpleasant (-) or pleasant (+) rating in response to `How do you feel about your partners' contribution?` (range -250 to +250)
- `arousal`:  low (-) or high (+) rating in response to `How do you feel about your partners' contribution?` (range -250 to +250)
- `sub_contribution`: the amount of money given to the common good by the subject, ranges from 0 - 1 in increments of `.1`.
- `sub_contribution_binary`: `sub_contribution` was converted into a binary variable with defect (0 - .49) and cooperate (.50 - 1). 
- `study`: refers to whether the data was from the `ug`, `pd`, or `pgg` experiment

```{r read_data}
# Load
df_emotion <- read_csv(str_c(dir_clean_data, "/emo_classify_all.csv"))
df_ug <- read_csv(str_c(dir_clean_data, "/ug_data.csv"))
df_pgg <- read_csv(str_c(dir_clean_data, "/pgg_data.csv"))
df_pd <- read_csv(str_c(dir_clean_data, "/pd_data.csv"))

# Glimpse of data
head(df_emotion) %>%
  kable(caption = "Emotion Classification Glimpse") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

head(df_ug) %>%
  kable(caption = "Ultimatum Game Glimpse") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

head(df_pd) %>%
  kable(caption = "Prisoners' Dilemma Glimpse") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

head(df_pgg) %>%
  kable(caption = "Public Goods Game Glimpse") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

# Figure 1 - Methods

```{r fig1}
# Emotion list
emotion_list <- c("neutral", "surprised", "aroused", "peppy", "enthusiastic", "happy", "satisfied", "relaxed", "calm", "sleepy", "still", "quiet", "sluggish", "sad", "disappointed", "disgusted", "annoyed", "angry", "afraid", "nervous")

plot_width = 6
plot_height = 6

fig1_data <- df_emotion %>%
  mutate(emotion = fct_relevel(emotion, emotion_list))

emotion_theme <- theme_bw() + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        aspect.ratio = 1, 
        axis.text.x = element_text(size = 22), 
        axis.text.y = element_text(size = 22),
        axis.title = element_text(size = 26), 
        legend.position = "none")

# Fig1a - Blank (not used)
fig1a_plot <- ggplot(fig1_data, aes(x = valence, y = arousal, color = emotion)) + 
  geom_point(alpha = 0) +
  geom_hline(yintercept = 0) + 
  geom_vline(xintercept = 0) +
  coord_fixed() + # square
  scale_y_continuous(name = "Arousal", breaks = seq(-200, 200, by = 100)) +
  scale_x_continuous(name = "Valence", breaks = seq(-200, 200, by = 100)) +
  emotion_theme
fig1a_plot

ggsave(filename = str_c(dir_graphs, "/figure1/fig1a.pdf"), plot=fig1a_plot, width = plot_width, height = plot_height)

# Fig1b - All points
fig1b_plot <- ggplot(fig1_data, aes(x = valence, y = arousal, color = emotion)) + 
  geom_point(alpha = .5) +
  geom_hline(yintercept = 0) + 
  geom_vline(xintercept = 0) +
  coord_fixed() + # square
  scale_y_continuous(name = "Arousal", breaks = seq(-200, 200, by = 100)) +
  scale_x_continuous(name = "Valence", breaks = seq(-200, 200, by = 100)) +
  emotion_theme
fig1b_plot

ggsave(filename = str_c(dir_graphs, "/figure1/fig1b.pdf"), plot=fig1b_plot, width = plot_width, height = plot_height)
ggsave(filename = str_c(dir_graphs, "/figure1/fig1b.png"), plot=fig1b_plot, width = plot_width, height = plot_height)


# Fig1c (not used)
fig1c_data <- df_emotion %>% 
  mutate(emotion = fct_relevel(emotion, emotion_list)) %>% 
  group_by(emotion) %>%
  dplyr::summarise(meanValence = mean(valence), meanArousal = mean(arousal),
                   sdValence = sd(valence), sdArousal = sd(arousal), N = n(), 
                   seValence = sdValence / sqrt(N), seArousal = sdArousal / sqrt(N)) %>%
  mutate(ciLowerValence = meanValence - qt(1 - (0.05 / 2), N - 1) * seValence,
         ciUpperValence = meanValence + qt(1 - (0.05 / 2), N - 1) * seValence, 
         ciLowerArousal = meanArousal - qt(1 - (0.05 / 2), N - 1) * seArousal,
         ciUpperArousal = meanArousal + qt(1 - (0.05 / 2), N - 1) * seArousal)

fig1c_plot <- ggplot(fig1_data, aes(x = valence, y = arousal, color = emotion)) + geom_point(alpha = .05) + # all data points
  geom_point(data = fig1c_data, aes(x = meanValence, y = meanArousal, color = emotion), size = 2) + # averages
  geom_errorbar(data = fig1c_data, aes(x = meanValence, y = meanArousal, ymin = ciLowerArousal, ymax = ciUpperArousal)) + # CIs
  geom_errorbarh(data = fig1c_data, aes(x = meanValence, y = meanArousal, xmin = ciLowerValence, xmax = ciUpperValence)) + # CIs
  geom_text_repel(data = fig1c_data, aes(x = meanValence, y = meanArousal, color = emotion, label = emotion), segment.colour = NA, force = 10, show.legend = FALSE, size = 5) + 
  geom_hline(yintercept = 0) + 
  geom_vline(xintercept = 0) +
  coord_fixed() +
  scale_y_continuous(name = "Arousal", breaks = seq(-200, 200, by = 100)) +
  scale_x_continuous(name = "Valence", breaks = seq(-200, 200, by = 100)) +
  emotion_theme
fig1c_plot

ggsave(filename = str_c(dir_graphs, "/figure1/fig1c.pdf"), plot=fig1c_plot, width = plot_width, height = plot_height)

# If you want the colors used
colorFig <- ggplot(fig1c_data, aes(x = meanValence, y = meanArousal, color = emotion)) + 
  geom_point()
color <- ggplot_build(colorFig)
colorLabels <- unique(color$data[[1]]["colour"])

# Fig1d - Ultimatum Game
fig1d_data <- df_ug %>%
  mutate(choice_fct = case_when(choice == 0 ~ "Accept", choice == 1 ~ "Punish"))

fig1d_plot <- ggplot(fig1d_data, aes(x = valence, y = arousal, color = choice_fct)) + 
  geom_point(alpha = .5) +
  geom_hline(yintercept = 0) + 
  geom_vline(xintercept = 0) +
  coord_fixed() + # square
  scale_y_continuous(name = "Arousal", breaks = seq(-200, 200, by = 100)) +
  scale_x_continuous(name = "Valence", breaks = seq(-200, 200, by = 100)) +
  scale_color_manual(values = c("#00BFC4", "#F8766D")) + 
  emotion_theme
fig1d_plot

ggsave(filename = str_c(dir_graphs, "/figure1/fig1d.pdf"), plot=fig1d_plot, width = plot_width, height = plot_height)
ggsave(filename = str_c(dir_graphs, "/figure1/fig1d.png"), plot=fig1d_plot, width = plot_width, height = plot_height)
```

# Figure 2 - Machine learning approaches

```{r fig2}
## Evaluate overall model accuracy (loading models takes a long time)
nn_fit <- readRDS(str_c(dir_data, "/models/nn_model.RDS"))
knn_fit <- readRDS(str_c(dir_data, "/models/knn_model.RDS"))
svm_fit <- readRDS(str_c(dir_data, "/models/svm_model.RDS"))
df_train <- read_csv(str_c(dir_data, "/models/df_train.csv"))
df_test <- read_csv(str_c(dir_data, "/models/df_train.csv"))

# Calculating out of sample accuracy
df_test_nn <- df_test %>% 
  mutate(nn_class = predict(nn_fit, newdata = df_test, type = "raw"))
nn_cm <- caret::confusionMatrix(table(df_test_nn$nn_class, df_test_nn$emotion))

df_test_svm <- df_test %>% 
  mutate(svm_class = predict(svm_fit, newdata = df_test, type = "raw"))
svm_cm <- caret::confusionMatrix(table(df_test_svm$svm_class, df_test_svm$emotion))

df_test_knn <- df_test %>% 
  mutate(knn_class = predict(knn_fit, newdata = df_test, type = "raw"))
knn_cm <- caret::confusionMatrix(table(df_test_knn$knn_class, df_test_knn$emotion))

# Accuracy
nn_cm$overall
svm_cm$overall
knn_cm$overall

# Figures 2a - 2c: Model views
## NN model view
nn_emo_space <- expand.grid(valence = seq(-250, 250, by = 1), 
                            arousal = seq(-250, 250, by = 1))
nn_emo_space$class <- predict(nn_fit, newdata = nn_emo_space, type = "raw") # emo class

fig2a_plot <- ggplot() + 
  geom_point(data = nn_emo_space, aes(x = valence, y = arousal, color = class), size = 1, alpha = 1) + 
  scale_x_continuous(name = "Valence", limits = c(-250, 250)) + 
  scale_y_continuous(name = "Arousal", limits = c(-250, 250)) + 
  geom_hline(yintercept = 0) + 
  geom_vline(xintercept = 0) +
  scale_color_discrete(name = "Predicted Emotion") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        axis.ticks = element_blank(), axis.text = element_blank(), text = element_text(size = 14), aspect.ratio = 1)
fig2a_plot

ggsave(filename=str_c(dir_graphs, "/figure2/model_vision/fig2a_nn.pdf"), fig2a_plot + theme(legend.position = "none"), width = 6, height = 6, useDingbats=F)
ggsave(filename=str_c(dir_graphs, "/figure2/model_vision/fig2a_nn.png"), fig2a_plot + theme(legend.position = "none"), width = 6, height = 6)
ggsave(filename=str_c(dir_graphs, "/figure2/model_vision/fig2_legend.pdf"), cowplot::get_legend(fig2a_plot), height = 6, useDingbats=F)

# Figure 2d: Probabilistic representation for NN
nn_emo_probs_raw <- expand.grid(valence = seq(-250, 250, by = 1), 
                                arousal = seq(-250, 250, by = 1))
nn_probs <- predict(nn_fit, newdata = nn_emo_probs_raw, type = "prob")

nn_emo_probs <- bind_cols(nn_emo_probs_raw, nn_probs) %>%
  pivot_longer(cols = afraid:surprised, names_to = "nn_emotion", values_to = "nn_probs")

fig2d_plot <- ggplot(data = nn_emo_probs, aes(x = valence, y = arousal, color = nn_probs, group = nn_emotion)) + 
  geom_point(size = 1) + 
  scale_x_continuous(name = "Valence", limits = c(-250, 250)) + 
  scale_y_continuous(name = "Arousal", limits = c(-250, 250)) + 
  facet_wrap(~nn_emotion, ncol = 4) + 
  geom_hline(yintercept = 0) + 
  geom_vline(xintercept = 0) +
  scale_color_gradient(low = "white", high = "blue", name = "NN Probability", labels = scales::percent) + 
  theme_bw() +  
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        axis.ticks = element_blank(), axis.text = element_blank(), text = element_text(size = 14), aspect.ratio = 1)
fig2d_plot
ggsave(filename=str_c(dir_graphs, "/figure2/model_vision/fig2d_nn.png"), fig2d_plot, width = 8, height = 8, limitsize=F)

## KNN model view
knn_emo_space <- expand.grid(valence = seq(-250, 250, by = 1), 
                             arousal = seq(-250, 250, by = 1))
knn_emo_space$class <- predict(knn_fit, newdata = knn_emo_space, type = "raw") # emo class

fig2b_plot <- ggplot() + 
  geom_point(data = knn_emo_space, aes(x = valence, y = arousal, color = class), size = 1, alpha = 1) + 
  scale_x_continuous(name = "Valence", limits = c(-250, 250)) + 
  scale_y_continuous(name = "Arousal", limits = c(-250, 250)) + 
  geom_hline(yintercept = 0) + 
  geom_vline(xintercept = 0) +
  scale_color_discrete(name = "Predicted Emotion") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        axis.ticks = element_blank(), axis.text = element_blank(), text = element_text(size = 14), aspect.ratio = 1)
fig2b_plot

ggsave(filename=str_c(dir_graphs, "/figure2/model_vision/fig2b_knn.pdf"), fig2b_plot + theme(legend.position = "none"), width = 6, height = 6, useDingbats=F)
ggsave(filename=str_c(dir_graphs, "/figure2/model_vision/fig2b_knn.png"), fig2b_plot + theme(legend.position = "none"), width = 6, height = 6)

## SVM model view
svm_emo_space <- expand.grid(valence = seq(-250, 250, by = 1), 
                             arousal = seq(-250, 250, by = 1))
svm_emo_space$class <- predict(svm_fit, newdata = svm_emo_space, type = "raw") # emo class

fig2c_plot <- ggplot() + 
  geom_point(data = svm_emo_space, aes(x = valence, y = arousal, color = class), size = 1, alpha = 1) + 
  scale_x_continuous(name = "Valence", limits = c(-250, 250)) + 
  scale_y_continuous(name = "Arousal", limits = c(-250, 250)) + 
  geom_hline(yintercept = 0) + 
  geom_vline(xintercept = 0) +
  scale_color_discrete(name = "Predicted Emotion") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        axis.ticks = element_blank(), axis.text = element_blank(), text = element_text(size = 14), aspect.ratio = 1)
fig2c_plot

ggsave(filename=str_c(dir_graphs, "/figure2/model_vision/fig2c_svm.pdf"), fig2c_plot + theme(legend.position = "none"), width = 6, height = 6, useDingbats=F)
ggsave(filename=str_c(dir_graphs, "/figure2/model_vision/fig2c_svm.png"), fig2c_plot + theme(legend.position = "none"), width = 6, height = 6)

#rm(nn_fit) # optional
#rm(knn_fit) # optional
#rm(svm_fit) # optional
```

# Figure 3 - Emotion classification contours and densities

```{r fig3}
# Aesthetics
emotion_list <- c("neutral", "surprised", "aroused", "peppy", "enthusiastic", "happy", "satisfied", "relaxed", "calm", "sleepy", "still", "quiet", "sluggish", "sad", "disappointed", "disgusted", "annoyed", "angry", "afraid", "nervous")

emotion_theme <- theme_bw() + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        aspect.ratio = 1, 
        axis.text.x = element_text(size = 14), 
        axis.text.y = element_text(size = 14),
        axis.title = element_text(size = 24), 
        legend.position = "none")

# Fig3 data
fig3_data <- df_emotion %>%
  mutate(emotion = fct_relevel(emotion, emotion_list)) %>% ungroup()

# Figure 3a - Contour Plots (separate density levels per plot)
fig3a_list <- list()

# Loop through each emotion dataset and make a contour plot
for (i in 1:length(emotion_list)) {
  # Filter data
  plot_data <- fig3_data %>% filter(emotion == emotion_list[i]) 
  
  # Plot
  plot <- ggplot(plot_data,  aes(x = valence, y = arousal, color = emotion)) + 
    geom_density_2d() + 
    geom_hline(yintercept = 0, color = "black") + 
    geom_vline(xintercept = 0, color = "black") +
    scale_color_manual(values = colorLabels$colour[i]) +  # pull colors from Figure 1
    coord_fixed(ratio = 1) +
    scale_y_continuous(limits = c(-250, 250)) + 
    scale_x_continuous(limits = c(-250, 250)) + 
    #scale_y_continuous(name = "Arousal", breaks = seq(-200, 200, by = 100)) +
    #scale_x_continuous(name = "Valence", breaks = seq(-200, 200, by = 100)) +
    ggtitle(emotion_list[i]) + 
    theme_bw() + 
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(), 
          plot.margin = unit(c(-.1, -.1, -.1, -.1), "cm"),  # plot margins (top, right, bottom, left)
          plot.title = element_text(hjust = 0.5, vjust = -1.5),   # center title, put on top of graph
          axis.text = element_blank(), 
          axis.ticks = element_blank(),
          axis.title = element_blank(), 
          legend.position = "none")
  
  # Add to list
  fig3a_list[[i]] <- ggplotGrob(plot)
}

fig3a_plot <- cowplot::plot_grid(plotlist=fig3a_list, ncol=4)
fig3a_plot
ggsave(filename = str_c(dir_graphs, "/figure3/fig3a.pdf"), plot=fig3a_plot, width = 6, height = 6)

# Figure 3b - 1D density
fig3b_plot <- ggplot(fig3_data %>% pivot_longer(cols = c(valence, arousal), names_to = "measure", values_to = "value"),
                      aes(x = value, y = emotion, fill = emotion)) +
  ggridges::geom_density_ridges(scale = 3, alpha = 3/4, bandwidth = 18) +  # tweek to visualize
  scale_x_continuous() +
  facet_wrap(~measure) +
  theme_bw(base_size=9) +
  theme(axis.text = element_text(size = 14),
        axis.title = element_text(size = 16),
        strip.text = element_text(size = 14),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = "none")
fig3b_plot
ggsave(filename = str_c(dir_graphs, "/figure3/fig3b.pdf"), plot=fig3b_plot, width = 6, height = 8)
```

# Figure 4 and Figure 6 - NN Emotion Classifications

```{r fig4}
# Requires model 
nn_fit <- readRDS(str_c(dir_data, "/models/nn_model.RDS"))
ug_nn <- predict(nn_fit, newdata = df_ug, type = "prob")
df_ug_probs <- df_ug %>% bind_cols(ug_nn)
rm(nn_fit) # helpful for memory

# Fig4 data
fig4a_data <- df_ug_probs %>%
  select(sub, choice, afraid:surprised) %>%
  pivot_longer(cols = -c(sub, choice), names_to = "nn_emotion", values_to = "nn_prob") %>%
  group_by(choice, nn_emotion, sub) %>%
  summarise(mean_prob_sub = mean(nn_prob)) %>%
  group_by(choice, nn_emotion) %>% 
  summarise(mean_prob = mean(mean_prob_sub), sd_prob = sd(mean_prob_sub), N = n(), se_prob = sd_prob / sqrt(N)) %>%
  mutate(lwr = mean_prob - qt(1 - (0.05 / 2), N - 1) * se_prob,
         upr = mean_prob + qt(1 - (0.05 / 2), N - 1) * se_prob, 
         choice = case_when(choice == 0 ~ "Accept", choice == 1 ~ "Punish")) %>%
  # Add numeric labels
  mutate(label = str_c(as.character(round(mean_prob*100, 1)), "%"), 
         y_label = mean_prob + .04)

# Top emotions
fig4a_data %>% mutate_if(is.numeric, round, 4) %>% group_by(choice) %>% arrange(desc(mean_prob))

#### Figure 4a
# Fig4a plot - probabilities by choice
label_size <- 4
label_color <- "dark gray"
fig4a_plot <- ggplot(fig4a_data, aes(x = tidytext::reorder_within(nn_emotion, mean_prob, choice), y = mean_prob, fill = nn_emotion)) + 
  geom_col(show.legend = FALSE) + 
  geom_errorbar(aes(ymin = lwr, ymax = upr), width = .1) + 
  geom_text(aes(label = label, y = y_label), color = label_color, size = label_size) + 
  facet_wrap(~choice, scales = "free_y") + 
  scale_y_continuous(labels = scales::label_percent(accuracy = 1L), name = "Model Likelihood", limits = c(0, .20)) +
  coord_flip() + 
  tidytext::scale_x_reordered(name = "NN Emotion") + 
  theme_classic() + 
  theme(text = element_text(size = 14))
fig4a_plot
ggsave(filename=str_c(dir_graphs, "/figure4/fig4a.pdf"), fig4a_plot, width = 6, height = 4, useDingbats=F)

# Fig4a t-tests
fig4a_data_tests <- df_ug_probs %>%
  select(sub, choice, afraid:surprised) %>%
  pivot_longer(cols = -c(sub, choice), names_to = "nn_emotion", values_to = "nn_prob") %>%
  group_by(choice, nn_emotion, sub) %>%
  summarise(mean_prob_sub = mean(nn_prob)) %>%
  mutate(choice = case_when(choice == 0 ~ "Accept", choice == 1 ~ "Punish")) %>% ungroup()

## Top three vs angry
fig4a_tests1 <- fig4a_data_tests %>%
  filter(choice == "Punish", nn_emotion %in% c("sad", "angry")) %>%
  t_test(mean_prob_sub ~ nn_emotion, paired = TRUE) %>%
  add_significance() %>%
  bind_cols(fig4a_data_tests %>% 
             filter(choice == "Punish", nn_emotion %in% c("sad", "angry")) %>%
             cohens_d(mean_prob_sub ~ nn_emotion, paired = TRUE) %>% select(effsize))

fig4a_tests2 <- fig4a_data_tests %>%
  filter(choice == "Punish", nn_emotion %in% c("disappointed", "angry")) %>%
  t_test(mean_prob_sub ~ nn_emotion, paired = TRUE) %>%
  add_significance() %>%
  bind_cols(fig4a_data_tests %>% 
             filter(choice == "Punish", nn_emotion %in% c("disappointed", "angry")) %>%
             cohens_d(mean_prob_sub ~ nn_emotion, paired = TRUE) %>% select(effsize))

fig4a_tests3 <- fig4a_data_tests %>%
  filter(choice == "Punish", nn_emotion %in% c("disgusted", "angry")) %>%
  t_test(mean_prob_sub ~ nn_emotion, paired = TRUE) %>%
  add_significance() %>%
  bind_cols(fig4a_data_tests %>% 
             filter(choice == "Punish", nn_emotion %in% c("disgusted", "angry")) %>%
             cohens_d(mean_prob_sub ~ nn_emotion, paired = TRUE) %>% select(effsize))

fig4a_tests_all <- bind_rows(fig4a_tests1, fig4a_tests2, fig4a_tests3)
fig4a_tests_all

### Figure 4b - Delta (Punish - Choice) by Emotion
fig4b_data <- df_ug_probs %>%
  select(sub, choice, afraid:surprised) %>%
  pivot_longer(cols = -c(sub, choice), names_to = "nn_emotion", values_to = "nn_prob") %>%
  group_by(choice, nn_emotion, sub) %>%
  summarise(mean_prob_sub = mean(nn_prob)) %>%
  group_by(choice, nn_emotion) %>% 
  summarise(mean_prob = mean(mean_prob_sub), sd_prob = sd(mean_prob_sub), N = n(), se_prob = sd_prob / sqrt(N)) %>%
  mutate(lwr = mean_prob - qt(1 - (0.05 / 2), N - 1) * se_prob,
         upr = mean_prob + qt(1 - (0.05 / 2), N - 1) * se_prob, 
         choice = case_when(choice == 0 ~ "Accept", choice == 1 ~ "Punish")) %>%
  # Delta
  select(choice, nn_emotion, mean_prob) %>%
  pivot_wider(names_from = choice, values_from = mean_prob) %>% 
  group_by(nn_emotion) %>% 
  mutate(delta = Punish - Accept) %>%
  # Add numeric labels
  mutate(label = str_c(as.character(round(delta*100, 1)), "%"), 
         y_label = if_else(delta >= 0, delta + .03, delta - .03))

# Fig 4b Plot
fig4b_plot <- ggplot(fig4b_data, aes(x = reorder(nn_emotion, delta), y = delta, fill = nn_emotion)) + 
  geom_col(show.legend = FALSE, position = position_dodge(.9)) + 
  geom_text(aes(label = label, y = y_label), color = label_color, size = label_size) + 
  scale_y_continuous(labels = scales::percent, name = "Model Likelihood (Punish - Accept)", expand = c(.03, .03)) +
  xlab("NN Emotion") + 
  theme_classic() + 
  coord_flip() + 
  theme(text = element_text(size = 14))
fig4b_plot
ggsave(filename=str_c(dir_graphs, "/figure4/fig4b.pdf"), fig4b_plot, width = 6, height = 4, useDingbats=F)

### Fig 4 All
fig4_plot <- cowplot::plot_grid(fig4a_plot, fig4b_plot, labels = c("A", "B"), nrow = 1, rel_widths = c(3, 2))
ggsave(filename=str_c(dir_graphs, "/figure4/fig4.pdf"), fig4_plot, width = 10, height = 4, useDingbats=F)

### Figure 6 - Unfairness
# fig6 data
fig6_data <- df_ug_probs %>%
  select(sub, choice, afraid:surprised, unfairness) %>%
  pivot_longer(cols = -c(sub, choice, unfairness), names_to = "nn_emotion", values_to = "nn_prob") %>%
  group_by(choice, nn_emotion, sub, unfairness) %>%
  summarise(mean_prob_sub = mean(nn_prob)) %>%
  mutate(choice = case_when(choice == 0 ~ "Accept", choice == 1 ~ "Punish")) %>%
  group_by(choice, nn_emotion, unfairness) %>%
  summarise(mean_prob = mean(mean_prob_sub))

# Top emotion per unfairness bin for punish
fig6_data %>% mutate_if(is.numeric, round, 4) %>% filter(choice == "Punish") %>% group_by(unfairness) %>% top_n(mean_prob, n = 1) %>% arrange(desc(unfairness))

# Top emotions for highest unfairness
fig6_data %>% mutate_if(is.numeric, round, 4) %>% filter(choice == "Punish", unfairness == .95) %>% arrange(desc(mean_prob))

# Fig 6 Plot
fig6_plot <- ggplot(fig6_data, aes(x = unfairness, y = mean_prob, fill = nn_emotion)) + 
  geom_bar(position = "fill", stat = "identity") + 
  facet_wrap( ~ choice) + 
  xlab("Unfairness") + 
  scale_y_continuous(labels = scales::percent, name = "Proportion") + 
  theme_classic() + 
  theme(text = element_text(size = 14))
fig6_plot
ggsave(filename=str_c(dir_graphs, "/figure6/fig6.pdf"), fig6_plot, width = 8, height = 6, useDingbats=F)

# t-test for fairness
fig6_data_tests <- df_ug_probs %>%
  select(sub, choice, afraid:surprised, unfairness) %>%
  pivot_longer(cols = -c(sub, choice, unfairness), names_to = "nn_emotion", values_to = "nn_prob") %>%
  group_by(choice, nn_emotion, sub, unfairness) %>%
  summarise(mean_prob_sub = mean(nn_prob)) %>%
  mutate(choice = case_when(choice == 0 ~ "Accept", choice == 1 ~ "Punish")) %>% ungroup()

fig6_tests1 <- fig6_data_tests %>%
  filter(choice == "Punish", unfairness == .95, nn_emotion %in% c("sad", "angry")) %>%
  t_test(mean_prob_sub ~ nn_emotion, paired = TRUE) %>%
  add_significance() %>%
  bind_cols(fig6_data_tests %>% 
             filter(choice == "Punish", unfairness == .95, nn_emotion %in% c("sad", "angry")) %>%
             cohens_d(mean_prob_sub ~ nn_emotion, paired = TRUE) %>% select(effsize))

fig6_tests2 <- fig6_data_tests %>%
  filter(choice == "Punish", unfairness == .95, nn_emotion %in% c("disgusted", "angry")) %>%
  t_test(mean_prob_sub ~ nn_emotion, paired = TRUE) %>%
  add_significance() %>%
  bind_cols(fig6_data_tests %>% 
             filter(choice == "Punish", unfairness == .95, nn_emotion %in% c("disgusted", "angry")) %>%
             cohens_d(mean_prob_sub ~ nn_emotion, paired = TRUE) %>% select(effsize))

fig6_tests_all <- bind_rows(fig6_tests1, fig6_tests2)
fig6_tests_all
```

# Figure 5 - KMeans Clustering Approach

```{r fig5}
# Requires model 
kmeans_fit <- readRDS(str_c(dir_data, "/models/kmeans_model.RDS"))

# Fig5a: What K-means "sees"
fig5a_data <- expand.grid(valence = seq(-250, 250, by = 1), 
                         arousal = seq(-250, 250, by = 1))
fig5a_data$class <- clue::cl_predict(kmeans_fit, newdata = fig5a_data)

fig5a_plot <- ggplot() + 
  geom_point(data = fig5a_data, aes(x = valence, y = arousal, color = as.factor(class)), size = 1, alpha = 1) + 
  scale_x_continuous(name = "Valence", limits = c(-250, 250)) + 
  scale_y_continuous(name = "Arousal", limits = c(-250, 250)) + 
  geom_hline(yintercept = 0) + 
  geom_vline(xintercept = 0) +
  scale_color_discrete(name = "Predicted Class") +
  theme_bw() +  
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        axis.ticks = element_blank(), axis.text = element_blank(), text = element_text(size = 14), aspect.ratio = 1)
fig5a_plot
ggsave(filename=str_c(dir_graphs, "/figure5/fig5a.pdf"), fig5a_plot + theme(legend.position = "none"), width = 6, height = 6, useDingbats=F)
ggsave(filename=str_c(dir_graphs, "/figure5/fig5a.png"), fig5a_plot + theme(legend.position = "none"), width = 6, height = 6)


# Fig5b: Modal emotion in each region
df_emotion$kmean_cluster <-  clue::cl_predict(kmeans_fit, newdata = df_emotion[,c("valence", "arousal")])

# Reference totals
ref_totals <- df_emotion %>%
  group_by(kmean_cluster, emotion) %>%
  count() %>% 
  group_by(kmean_cluster) %>% 
  summarise(total = sum(n))

fig5b_data <- df_emotion %>%
  group_by(kmean_cluster, emotion) %>%
  count() %>% 
  group_by(kmean_cluster) %>% 
  slice_max(order_by = n, n = 1) %>%
  left_join(., ref_totals, by = "kmean_cluster") %>%
  mutate(prop = n / total) %>%
  # Add labels
  mutate(label = str_c(as.character(round(prop*100, 1)), "%"), 
         y_label = prop + .02)

label_size <- 4
label_color <- "dark gray"

fig5b_plot <- ggplot(data = fig5b_data, aes(x = as.factor(kmean_cluster), y = prop, fill = as.factor(kmean_cluster))) + 
  geom_col() +
  geom_text(aes(label = label, y = y_label), color = label_color, size = label_size-1) + 
  xlab(label = "KMeans Cluster") + 
  scale_y_continuous(name = "% of Cluster", label = scales::percent) + 
  scale_fill_discrete(name = "Modal Emotion") +
  theme_classic() + 
  theme(text = element_text(size = 26))
fig5b_plot
ggsave(filename=str_c(dir_graphs, "/figure5/fig5b.pdf"), fig5b_plot, width = 8, height = 4, useDingbats=F)


# Fig5c: Ultimatum Game Results
ug_kmeans <- clue::cl_predict(kmeans_fit, newdata = df_ug[c("valence", "arousal")], type = "class_ids")
df_ug_probs <- df_ug %>% mutate(kmeans_cluster = ug_kmeans)

fig5c_data <- df_ug_probs %>%
  group_by(choice, kmeans_cluster) %>%
  summarise(N = n()) %>%
  mutate(freq = N / sum(N), 
         choice = case_when(choice == 0 ~ "Accept", 
                            choice == 1 ~ "Punish")) %>%
  # Add labels
  mutate(label = str_c(as.character(round(freq*100, 1)), "%"), 
         y_label = freq + .06)

# Plot
fig5c_plot <- ggplot(fig5c_data, 
                     aes(x = tidytext::reorder_within(kmeans_cluster, freq, choice), y = freq, fill = as.factor(kmeans_cluster))) + 
  geom_col(show.legend = FALSE) + 
  geom_text(aes(label = label, y = y_label), color = label_color, size = label_size) + 
  facet_wrap(~choice, scales = "free_y") + 
  scale_y_continuous(labels = scales::label_percent(accuracy = 1L), name = "Frequency", limits = c(0, .5)) +
  coord_flip() + 
  tidytext::scale_x_reordered(name = "KMeans Cluster") + 
  theme_classic() + 
  theme(text = element_text(size = 14))
fig5c_plot
ggsave(filename=str_c(dir_graphs, "/figure5/fig5c.pdf"), fig5c_plot, width = 6, height = 4, useDingbats=F)

# Tests
## Punish
kmeans_t1 <- as.table(rbind(c(1612, 831))) # Punish 3 vs Punish 1
dimnames(kmeans_t1) <- list(irrelevant = c("A"), cluster = c("3", "1"))
chisq.test(kmeans_t1)

## Accept
kmeans_t2 <- as.table(rbind(c(3865, 2103))) # Accept 5 vs Accept 2
dimnames(kmeans_t2) <- list(irrelevant = c("A"), cluster = c("5", "2"))
chisq.test(kmeans_t2)
```

# Euclidean distance analysis

```{r euclid}
# Calculate, participant-by-participant, the Euclidean distance between their emotion classification words and UG
dist_trial <- function(df_emotion_sub, trial_valence, trial_arousal) {
  
  probs <- df_emotion_sub %>% 
    mutate(dist = sqrt((valence - {{trial_valence}}) ^ 2 + (arousal - {{trial_arousal}}) ^ 2), # calculate distance
           dist = case_when(dist == 0 ~ 1, 
                            dist != 0 ~ dist), # Minimum distance needs to be one to avoid issues calculating prob
           prob = (1 / dist) / sum((1 / dist))) %>%    # calculate probability based on inverse (1 / distance) / (sum (1 / distance))
    select(emotion, prob) %>% 
    pivot_wider(names_from = emotion, values_from = prob)
  
  return(probs)
}

dist_analysis <- function(df_emotion_sub, df_behavior_sub) {
  
  ## Inputs: 
  # df_emotion_sub is all subject data for emotion classification task 
  # df_behavior_sub is all subject data for the behavioral game (ug, pd, or pgg) 
  
  # Initialize list
  data_list <- list() 
  
  for (row in 1:nrow(df_behavior_sub)) {
    trial_probs <- dist_trial(df_emotion_sub, trial_valence = df_behavior_sub$valence[row], trial_arousal = df_behavior_sub$arousal[row])
    data_list[[row]] <- trial_probs # add to list 
  }
  
  # Output
  df_probs <- do.call(rbind, data_list)
  return(df_probs)
}

# Ultimatum Game
df_euclidean_ug <- df_emotion %>% 
  filter(study == "ug") %>% 
  nest(data_emo = -sub) %>% 
  left_join(df_ug %>% nest(data_ug = -sub), by = "sub") %>% 
  group_by(sub) %>% 
  mutate(probs = map2(.x = data_emo, .y = data_ug, .f = dist_analysis)) %>%
  unnest(cols = c(data_ug, probs)) %>%
  select(-data_emo)

## Results
euclid_data <- df_euclidean_ug %>%
  select(sub, choice, annoyed:sad) %>%
  pivot_longer(cols = -c(sub, choice), names_to = "euclid_emotion", values_to = "euclid_prob") %>%
  group_by(choice, euclid_emotion, sub) %>%
  summarise(mean_prob_sub = mean(euclid_prob)) %>%
  group_by(choice, euclid_emotion) %>% 
  summarise(mean_prob = mean(mean_prob_sub), sd_prob = sd(mean_prob_sub), N = n(), se_prob = sd_prob / sqrt(N)) %>%
  mutate(lwr = mean_prob - qt(1 - (0.05 / 2), N - 1) * se_prob,
         upr = mean_prob + qt(1 - (0.05 / 2), N - 1) * se_prob, 
         choice = case_when(choice == 0 ~ "Accept", choice == 1 ~ "Punish"))

# T-tests
euclid_data_tests <- df_euclidean_ug %>%
  select(sub, choice, annoyed:sad) %>%
  pivot_longer(cols = -c(sub, choice), names_to = "euclid_emotion", values_to = "euclid_prob") %>%
  group_by(choice, euclid_emotion, sub) %>%
  summarise(mean_prob_sub = mean(euclid_prob)) %>%
  mutate(choice = case_when(choice == 0 ~ "Accept", choice == 1 ~ "Punish")) %>% ungroup()

## Top three vs angry
euclid_tests1 <- euclid_data_tests %>%
  filter(choice == "Punish", euclid_emotion %in% c("disgusted", "angry")) %>%
  t_test(mean_prob_sub ~ euclid_emotion, paired = TRUE) %>%
  add_significance() %>%
  bind_cols(euclid_data_tests %>% 
             filter(choice == "Punish", euclid_emotion %in% c("disgusted", "angry")) %>%
             cohens_d(mean_prob_sub ~ euclid_emotion, paired = TRUE) %>% select(effsize))

euclid_tests2 <- euclid_data_tests %>%
  filter(choice == "Punish", euclid_emotion %in% c("disappointed", "angry")) %>%
  t_test(mean_prob_sub ~ euclid_emotion, paired = TRUE) %>%
  add_significance() %>%
  bind_cols(euclid_data_tests %>% 
             filter(choice == "Punish", euclid_emotion %in% c("disappointed", "angry")) %>%
             cohens_d(mean_prob_sub ~ euclid_emotion, paired = TRUE) %>% select(effsize))

euclid_tests_all <- bind_rows(euclid_tests1, euclid_tests2)
euclid_tests_all
```

# See Supplement Analysis for PD and PGG